Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-22 ms.tex
I added the corner plot for the posterior distributions for the simple Mie model.
I added a reference for the forsterite index of refraction.

@@

We fit the variability amplitude spectrum with an optically thin Mie scattering model and find it is consistent with forsterite grains with sub-micron sized particles.
We use a constant n=1.67 - 0.006 $j$ index of refraction \citep{}.
A log-normal particle size distribution with a median of 0.2$\mu$m fits the data with a $\bar{\chi^2}$ of 2.5.
We also model the wavelength dependence with a spotted surface model with two different Planck functions covering different spatial regions.
The two temperature region model can fit variability amplitude spectrum well within errors, but gives implausible temperature differences.
Therefore, we favor the Mie scattering model as a better explanation for the variability amplitude spectrum.

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{corner_j1821_mie_sc.pdf}
\caption{Posterior distributions to the simple Mie scattering fit to the amplitude spectrum for \shb.
The model includes an amplitude offset, $B$, (to account for areal coverage) and a median particle radius, $r$.}\label{fig:ampspec1821mie}
\end{centering}
\end{figure}

@@

We fit the variability amplitude spectrum with an optically thin Mie scattering model and find it is consistent with forsterite (Mg$_2$SiO$_4$) grains with sub-micron sized particles.
We use a constant n=1.67 - 0.006 $j$ index of refraction because the real and imaginary parts of the index of refraction are relatively unchanged across the optical and near infrared \citep{scott1996forsterite}.
A log-normal particle size distribution with a median of 0.2$\mu$m fits the data with a $\bar{\chi^2}$ of 2.5.
We also model the wavelength dependence with a spotted surface model with two different Planck functions covering different spatial regions.
The two temperature region model can fit variability amplitude spectrum well within errors, but gives implausible temperature differences.
Therefore, we favor the Mie scattering model as a better explanation for the variability amplitude spectrum.
